\textit{Red Oak}\\ Proactive Controller Generation for Algorithmic Policy

### 2015-05-11 draft.tex
pseudocode

\begin{figure*}[ht]
\begin{lstlisting}[mathescape]
let compile (f: pkt $\rightarrow$ forwarding_decision) : policy =
      push most general packet to (empty) stack
      set the current location to be the root of an empty decision tree
      while (stack is not empty)
         pop the top of the stack as pkt
         run f of pkt resulting in a forwarding decision fd and a refined packet pkt
         record the forwarding decision for the symbolic packet pkt in the decision tree
         set the current location to be the root of the decision tree and repeat

\end{lstlisting}
\caption{Pseudocode for the compile function}
\label{fig:compile-pseudo}
\end{figure*}

@@

\begin{figure*}[ht]
\begin{lstlisting}
let run (pol: policy) (inputs: examples) : unit =
      build the symbolic rules for policy pol
      generate the concrete rules with all relations empty
      for each packets in input,
          find the first rule matching the packet, and record the forwarding decision fd
          if packet is sent to the controller then
              evaluate the policy on the packet, potentially updating relations
              regenerate concrete rules
              forward the packet according the evaluated forwarding decision
          else
              forward the packet according to fd 
\end{lstlisting}

\caption{Pseudocode for the run function}
\label{fig:run-pseudo}
  \end{figure*}

>>>>

\begin{figure}[ht]
\begin{lstlisting}[mathescape]
let compile (f: pkt $\rightarrow$ decision) : policy =
      stack $\gets$ empty.push(new packet)
      root $\gets$ new unexplored node
      while (stack is not empty)
          loc $\gets$ root
          pkt $\gets$ stack.pop
          fd $\gets$ f(pkt) 
          loc $\gets$ Leaf fd
      return root    
\end{lstlisting}
\caption{Pseudocode for the compile function}
\label{fig:compile-pseudo}
\end{figure}

@@

\begin{figure}[ht]
\begin{lstlisting}[mathescape]
let run (pol: policy) (inputs: examples) : unit =
      sr $\gets$ build_symbolic_rules(pol)
      rel $\gets$ empty
      cr $\gets$ build_concrete_rules(sr, rel)
      for each packets pkt in input,
      match evaluate_rules(cr, pkt) with
       | Some fd $\to$ Forward(pkt, fd)
       | None $\to$
           (fd, rel) $\gets$ evaluate_policy(pkt)
           cr $\gets$ build_concrete_rules(sr, rel)
           Forward(pkt, fd)     
\end{lstlisting}

\caption{Pseudocode for the run function}
\label{fig:run-pseudo}
  \end{figure}
